LAGOS lake depth

### 2020-02-20 README.Rmd
display markdown table data dictionaries

## LAGOS-US-Depth: Lake depth at continental scales

### Data (see [data/lagosus_depth.csv](data/lagosus_depth.csv))

```{r echo=FALSE}
# see scripts/99_make_taxonomy.R

dt <- read.csv("data/lagosus_depth_taxonomy.csv", stringsAsFactors = FALSE)

knitr::kable(setNames(dt, c("Variable name", "Description")))
```

@@

>>>>

## Bathymetry manuscript

@@

Data: [bathymetry derived lake depth](data/00_bathy_depth/00_bathy_depth.csv)

<details>
<summary>Data dictionary</summary>
```{r, echo=FALSE}
# see scripts/99_make_taxonomy.R

dt <- read.csv("data/00_bathy_depth/00_bathy_depth.csv", stringsAsFactors = FALSE)
knitr::kable(setNames(data.frame(names(dt)), "field")) 
```
</details> &nbsp;

Data: [bathymetry derived lake geometry](data/00_bathy_depth/bathy_geometry.csv)

<details>
<summary>Data dictionary</summary>
```{r, echo=FALSE}
# see scripts/99_make_taxonomy.R

dt <- read.csv("data/00_bathy_depth/bathy_geometry.csv", stringsAsFactors = FALSE)
knitr::kable(setNames(data.frame(names(dt)), "field"))
```
</details>
